\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}

\usepackage{../mystyle}

\usetikzlibrary{patterns,patterns.meta}

\title{Reider's Theorem, More and Less}
\author{}
\date{July 2026}

\DeclareMathOperator{\Kom}{Kom}
\DeclareMathOperator{\Cyl}{Cyl}
\DeclareMathOperator{\Stab}{Stab}
\DeclareMathOperator{\Slice}{Slice}
\DeclareMathOperator{\chern}{ch}
\DeclareMathOperator{\todd}{td}

\DeclareMathOperator{\Kos}{Kos}

\DeclareMathOperator{\ext}{ext}
%\DeclareMathOperator{\hom}{hom}

\newcommand{\cQ}{\mathcal{Q}}
\newcommand{\cZ}{\mathcal{Z}}
\newcommand{\LCom}{\mathcal{LC}}
\newcommand{\ft}{\text{ft}}
\newcommand{\Bl}{\mathrm{Bl}}
\newcommand{\Gr}{\mathrm{Gr}}

\newcommand{\rk}{\mathrm{rk}}

\newcommand{\cExt}{\mathcal{E}\hspace{-0.2em}xt}
\newcommand{\cTor}{\mathcal{T}\hspace{-0.2em}or}

\newcommand{\rddots}{\text{\reflectbox{$\ddots$}}}

\addbibresource{reider.bib}


\begin{document}

\maketitle

Let $S$ be a smooth projective surface over $\C$.

\section{Strategy}

Going back to the ideas of \cite{arcara_reiders_2009}, we will prove variants of Reider's theorem by finding suitable Bridgeland stability conditions.

Specifically, to show a line bundle $\omega_S(C)$ is $d$-very ample, we will get the vanishing
\[H^1(S,\cI_Z \otimes \omega_S(C)) = 0,\]
as $Z$ ranges over all length $d$ subschemes. This cohomology group can be rewritten (with the help of Serre duality) as
\begin{align*}
    \Ext_{\cO_S}^1(\cO_S(-C),\cI_Z \otimes \omega_S) &= \Ext_{\cO_S}^1(\cI_Z, \cO_S(-C))^\vee\\
    &= \Hom_{D^b(S)}(\cI_Z, \cO_S(-C)[1])^\vee.
\end{align*}
To preclude any nonzero morphism $\cI_Z\to \cO_S(-C)[1]$ in the derived category, we will then find a Bridgeland stability condition with $\cI_Z,\cO_S(-C)[1]$ both (semi)stable but such that $\cI_Z$ has greater slope.

{\color{red} Can we use this strategy to get Koszul cohomology to vanish by phrasing it as vanishing of cohomology of kernel bundles as in Ein-Lazarsfeld Theorem 5.2.5? This could work towards projective normality as in page 143?}
% \begin{rmk}
%     One might be interested in questions of syzygies and projective normality, and ask if this strategy could be pushed forward. Recall, the embedding $|K_S+C|$ (assuming it is an embedding) is \textit{projectively normal} if
%     \[\Sym^d H^0(S,\cO_S(1)) \twoheadrightarrow H^0(S,\omega_S^{\otimes d}(dC)).\]
%     For $d=1$, this automatic from $|K_S+C|$ being globally generated (since it is an embedding). 
% \end{rmk}

\section{Stability}

\subsection{Review}
We use notation from \cite{bertram_two_2026}, which includes a choice of smooth coordinates for a ``slice'' (of a chart) of the stability manifold. Specifically, we get a stability condition for each $(x,y)$ inside the parabola $x>\frac{1}{2}y^2$, which is the data of a central charge $Z_{(x,y)}$ and a heart of a bounded t-structure $\cA_{-y}$.
\begin{align*}
    Z_{(x,y)}(E) &= (-\chern_2(E), c_1(E) \cdot H) + (\rk E) (x,y)\\
    \cA_{-y} &= \{E \in D^b(S) \mid -\mu_{\min}(\cH^0(E)) < y \leq -\mu_{\max}(\cH^{-1}(E)), \; \cH^{i}(E)=0 \text{ for } i\neq -1,0\}
\end{align*}

We recall here that as we increase $y$, we make the following trade:
\begin{itemize}
    \item We \textit{gain} $H$-semistable coherent sheaves with low $H$-slope, like $\cO_S(-nC)$
    \item We \textit{lose} shifts of $H$-semistable coherent sheaves with low $H$-slope, like $\cO_S(-nC)[1]$.
\end{itemize}
In particular, an Mumford $H$-stable coherent sheaf $\cF$ appears in the category when $y>-\mu(\cF)$.

Note that when $\cF$ is \textit{not} $H$-semistable, we have to wait a while after we lose $\cF[1]$ before we gain $\cF$. For instance, on $\P^2$ for $\cF = \cO_{\P^2}(-1)\oplus \cO_{\P^2}(1)$, we have Harder-Narasimhan filtration
\[0 \leq \cO_{\P^2}(1) \leq \cO_{\P^2}(-1)\oplus\cO_{\P^2}(1),\]
so has maximal $H$-slope $\mu_{\max}(\cF) = 1$ and minimal slope $\mu_{\min}(\cF)=-1$. Therefore, $\cF[1]$ leaves the category once $y>-(1)$, but $\cF$ only joins the category once $y>-(-1)$.

Also important is a description of (numerical) walls, which are lines through \textit{points of indeterminacy} $I(E)$ of objects $E \in D^b(S)$, which are points $I(E)\in \R^2$ such that $Z_{I(E)}(E)=0$. These have coordinates
\[I(E) = \left(\frac{\chern_2 E}{\rk E}, -\mu\, E\right).\]
Any $H$-semistable coherent sheaf $\cF$ (or a shift, which has identical point of indeterminacy) has $I(\cF)$ outside or on the parabola---this a version of the Bogomolov inequality. Alternatively, we can rephrase this argument as follows: if $\cF$ is $H$-semistable, then $\cF \in \cA_{-\mu \cF}$ so it is in the category at $I(\cF)$, so $(x,y)$ cannot give a stability condition because the central charge sends an object to 0. Thus, $(x,y)$ is outside the parabola.

When $\cF$ fails to be semistable, like our example $\cF=\cO_{\P^2}(-1) \oplus \cO_{\P^2}(1)$, we might have $I(\cF)$ inside the parabola, but it will occur at a $y$ such that $\cF\not\in \cA_{-y}$. For example, for this $\cF$,

\[I(\cF) = \left(\frac{\chern_2(\cO_{\P^2}(-1))+\chern_2(\cO_{\P^2}(1))}{2}, \frac{-(-1)-(1)}{2}\right) = \left(\frac{1}{2}, 0\right),\]

and indeed, $\cO_{\P^2}(-1) \oplus \cO_{\P^2}(1) \not\in \cA_{0}$ as discussed earlier.



\subsection{\texorpdfstring{$\cO_S(-C)$}{O(-C)} and Bogomolov-sharp Sheaves}

Now, we analyze when $\cO_S(-C)[1]$ is (semi)stable. First, we describe how, for an $H$-semistable torsion free coherent sheaf $F$, might $F$ or $F[1]$ be destabilized. In particular, we need to know what a sub/quotient looks like in one of our hearts $\cA_{-y}$.

\begin{lem}\label{subs-and-quots-of-ss-sheaves-in-tilts}
    Let $F$ be as above. Then,
    \begin{enumerate}[label=(\arabic*)]
        \item If $K\leq F$ in $\cA_{-y}$ with cokernel $Q$, then, by the long exact sequence in $\Coh(S)$ cohomology,
        \[0\to \cH^{-1}(K) \to 0 \to \cH^{-1}(Q) \to \cH^0(K) \to F \to \cH^0(Q)\to 0\]
        $K$ is itself a sheaf with $\mu_{\min(K)}>-y$ (and torsion free, being an extension of $\cH^{-1}(Q)$ and a subsheaf of $F$).

        \item If $F[1] \twoheadrightarrow Q$ is a surjection in $\cA_{-y}$ with kernel $K$, then, by the long exact sequence in $\Coh(S)$ cohomology,
        \[0\to \cH^{-1}(K) \to F \to \cH^{-1}(Q) \to \cH^0(K) \to 0 \to \cH^0(Q)\to 0,\]
        $Q[-1]$ is itself a sheaf with $\mu_{\max}(Q[-1])\leq -y$ (so torsion free). {\color{red} check this... doesn't need $F$ torsion free?}
    \end{enumerate}
\end{lem}

\begin{lem}\label{H-slope-bound-for-destabilizers}
    Let $F$ be $H$-stable torsion free. Suppose there exists $(x,y)$ in the parabola such that $F$ is semistabilized by some proper subobject $E\xrightarrow{\phi} F$ in $\cA_{-y}$. Then, $(x,y)$ is above $I(E)$ above $I(F)$, i.e. $y > -\mu(E) > -\mu(F)$.
\end{lem}

% \begin{eg}
%     If $E\xrightarrow{\phi} F$ was a subobject in $\Coh(S)$, then the lemma is obvious by the stability of $F$. Furthermore, if $E$ was $H$-semistable, then $\mu(E) \leq \mu(\im_{\Coh(S)} E)$, and the chain of inequalities still gives us $\mu(E) < \mu(F)$. So, a good stress test might be the following composition
%     \[E=\cO \oplus \cO(1)^a \twoheadrightarrow \cO = F\]
%     which we denote $\phi:E\to F$, so that $\mu(E) = 1-\eps$ whereas $\mu(F) = 0$. To make this a subobject in some $\cA_{-y}$, we need the cone $F/E$ of $E\to F$ to be in $\cA_{-y}$, and since
%     \[\cH_{\Coh(S)}^{-1}(F/E) = \ker_{\Coh(S)} \phi,\]
%     this occurs exactly when the $\Coh(S)$ kernel $\cO(1)^a$ satisfies $-\mu_{\max}(\ker \phi) = -1 \geq y$. Thus, we have to choose $y\leq -1$ to make this a subobject, and we also need to choose $y>0$ to make $E$ part of the category. Thus, this isn't a counterexample. So, there is a tradeoff:
%     \begin{itemize}
%         \item To increase the slope of $E$ while still being a subobject of $F$ in $\cA_{-y}$, we need to make $E\to \im \phi$ a nontrivial $\Coh(S)$ quotient, and in fact this should be a quotient destabilizer so that $E$ can have bigger $H$-slope.
%         \item When $E$ becomes more $H$-unstable, it is harder for $E$ to be in the category $\cA_{-y}$.
%     \end{itemize}
%     We need to show that these two effects ``cancel out'', and force $-\mu(E) > -\mu(F)$.
% \end{eg}

\begin{proof}
    First, assume $\rk F > 0$, since otherwise the lemma is automatic. Continuing, since $E,F \in \cA_{-y}$, we know
    \[y> -\mu(F), -\mu_{\min}(E) \geq -\mu(E),\]
    so at least $(x,y)$ is above $I(E)$, $I(F)$.

    For $E\xrightarrow{\phi} F$ to be a monomorphism in $\cA_{-y}$, need the cone $C(\phi)\in \cA_{-y}$, which in particular means is the requirement that
    \[
        \mu_{\max}(\cH^{-1}(C(\phi))) = \mu_{\max}(\ker_{\Coh(S)} \phi) \leq -y
    \]
    Denote this kernel by $K$. If $K=0$, then $E$ injects in $F$ in $\Coh(S)$ and we win by $H$-stability of $F$. Otherwise, $K\neq 0$, is torsion free (by virtue of finite slope), so has positive rank. On the other extreme, we also cannot have $K=E$, since then
    \[\mu(E) \leq -y, \qquad \mu(E) > -y.\] 
    So, $E/K$ is nonzero. Now, we have short exact sequence in $\Coh(S)$
    \[0\to K \to E \to E/K\to 0,\]
    which gives
    \[H\cdot c_1(E) = H\cdot c_1(K) + H\cdot c_1(E/K), \tag{$\star$}\]
    and since $E/K \leq F$ is a nonzero subobject in $\Coh(S)$ with $F$ torsion free, we know $E/K$ is torsion free and
    \[1 \leq \rk E - \rk K \leq \rk F, \qquad \mu(E/K) < \mu(F).\]
    In particular, $\rk E\geq 1$, so it has finite $H$-slope, and we can use ($\star$) to solve for $\mu(E)$, giving us the equation
    \[\mu(E) = \frac{\rk(K)\mu(K)}{\rk E} + \frac{\rk(E/K) \mu(E/K)}{\rk E}.\]
    Plugging in our other inequalities, in particular using
    \[\mu(K) \leq -y < \mu(F)\]
    we get
    \begin{align*}
        \mu(E) &< \frac{\rk(K)}{\rk(E)}\mu(F) + \frac{\rk(E) - \rk(K)}{\rk(E)}\mu(F)\\
        &= \mu(F).\qedhere
    \end{align*}

    % {\color{red} Finally, we need to see that $I(E)$ is outside the parabola. AHHH!!! If $E$ is $H$-semistable, certainly this is true because $E[1]\in \cA_{-\mu(E)}$ is in the category at the height of $I(E[1])=I(E)$. Otherwise, if $E$ has a nontrivial Harder-Narasimhan filtration, there will be a nontrivial ``gap'' where $E$ is not in the category, and the gap contains the height $-\mu(E)$. So, this argument does \textit{not} work if $E$ is not $H$-semistable.
    
    % So, maybe I should argue that $\frac{\chern_2(E)}{\rk(E)}$ is sufficiently negative? I mean, I want the inequality
    % \begin{align*}
    %     x &\leq \frac{1}{2}y^2\\
    %     \frac{\chern_2(E)}{\rk(E)} &\leq \frac{1}{2}\mu(E)^2\\
    %     \chern_2(E) &\leq \frac{(H\cdot c_1(E))^2}{2\rk(E)}\\
    %     &\leq \frac{H^2 c_1(E)^2}{2\rk(E)} \tag{Hodge Index},
    % \end{align*}
    % but this is not obvious to me (and not clear if helpful...).
    % }
\end{proof}

\begin{lem}\label{between-parabola}
    With the same assumption as lemma \ref{H-slope-bound-for-destabilizers}, but also assuming $E$ is $(x,y)$-semistable, $I(E)$ is outside the parabola and on the same side of the parabola as $I(F)$.
\end{lem}
\begin{proof}
    $I(E)$ is outside of the parabola by a variant of the Bogomolov inequality for $(x,y)$ semistable objects ({\color{red} add reference/collect Bayer-Macr\`i-Toda theorem here too}). Then $(x,y)$ above $I(E)$ above $I(F)$ as in lemma \ref{H-slope-bound-for-destabilizers} implies the result.
\end{proof}

\begin{lem}\label{large-volume-limit}
    Let $F$ be an $H$-semistable torsion free sheaf. Then, $F$ is $(x,-\mu(F)+\eps)$ semistable for $x\gg 0$ and $0<\eps\ll 1$.
\end{lem}

\begin{proof}
    {\color{red} prove or cite this!! probably also need more in my applications to be careful...}
\end{proof}

\begin{lem}\label{destabilizing-wall-witness}
    Let $F$ be $(x,y)$-semistable such that in every neighborhood of $(x,y) \in \Stab(S)$, there exists an $(x',y')$ such that $F$ becomes unstable. Then, we can choose an $(x,y)$-semistable object $E$ with the same $(x,y)$ slope as $F$, such that $E$ is a subobject in $\cA_{-y}$ and such that $E\leq F$ destabilizes $F$ in some $(x',y')$ in any small neighborhood.
    
    Furthermore, the quotient $F/E$ in $\cA_{-y}$ is also $(x,y)$-semistable (this follows quickly).
\end{lem}

\begin{proof}
    {\color{red} state this lemma more carefully... do I need a requirement on the slope so that I can have a constant category somehow?} Choose a sequence $(x_n,y_n)$ converging to $(x,y)$, such that $F$ is $(x_n,y_n)$ unstable for all $n\in \N$, evidenced by a subobject $E_n \hookrightarrow F$ in $\cA_{-y_n}$. Even more, choose $E_n$ to be the first factor of the $(x_n,y_n)$ Harder-Narasimhan filtration, so that $E_n$ is $(x_n,y_n)$ semistable (and so this semistability spreads out in a neighborhood).
    
    Eventually, $E_n$ becomes a subobject in $\cA_{-y}$? Local finiteness of walls? Furthermore, the $\nu_{(x,y)}(E_n) \leq \nu_{(x,y)}(E)$ by virtue of the $(x,y)$-semistability of $E$, but for $n\gg 0$ we must get equality because $\nu_{(x,y)}(E_n)$ is continuous in $(x,y)$, and the inequality is reversed (and strict) at $(x_n,y_n)$. {\color{red} fix this later!!!}
\end{proof}

\begin{defn}
    As in lemma \ref{destabilizing-wall-witness}, we say
    \begin{itemize}
        \item the wall through $I(F)$ and $(x,y)$ is a \textbf{destabilizing wall} for $F$,
        \item the subobject $E\hookrightarrow F$ in $\cA_{-y}$ is a \textbf{witness} for the wall.
    \end{itemize}
\end{defn}

Now, we apply these lemmas to get the stability of $\cO_S(-C)[1]$ and friends, using the observation that
\[I(\cO_S(-C)[1]) = \left(\frac{C^2}{2}, \|C\|\right)\]
is exactly on the parabola. In this sense, $\cO_S(-C)[1]$ is \textit{Bogomolov-sharp} (the inequality became an equality), and we will show such Bogomolov-sharp object are stable in the following sense.

\begin{prop}
    Let $F\in \Coh(S)$ be $H$-stable and torsion free such that $I(F)$ lands on the parabola $x=\frac{1}{2}y^2$. Then,
    \begin{enumerate}[label=(\arabic*)]
        \item $F$ is $(x,y)$ semistable for all $(x,y)$ in the parabola with $y>-\mu(F)$.
        \item $F[1]$ is $(x,y)$ semistable for all $(x,y)$ in the parabola with $y\leq -\mu(F)$.
    \end{enumerate}
\end{prop}

\begin{proof}
    We show (1). By $H$-stability, $F$ will be $(x,-\mu(F)+\eps)$ semistable for $x\gg 0$ and $0<\eps \ll 1$ as in lemma \ref{large-volume-limit}, and $F$ will \textit{remain} $(x,y)$-semistable until just after a destabilizing wall for $F$ counterclockwise to the positive $x$-axis. Choose a witness
    \[0\to E \to F \to F/E \to 0\]
    for this wall, as in lemma \ref{destabilizing-wall-witness}. By lemma \ref{H-slope-bound-for-destabilizers} and \ref{between-parabola}, $I(F), I(E), (x,y)$ form a positive slope line with increasing heights in order with $I(E)$ outside the parabola, but this is impossible because the line segment $I(F)$ to $(x,y)$ is entirely inside the parabola. Thus, $I(F)$ couldn't have been destabilized.
\end{proof}

{\color{red} TODO: show (2) in a parallel way... might need to expand the lemmas though.}


\subsection{Ideal Sheaves}

Unlike $\cO_S(-C)[1]$, an ideal sheaf $\cI_Z$ for a length $d$ subscheme will not always be stable. However, we will establish numerical criteria to guarantee stability of the $\cI_Z$ long enough to find $(x,y)$ where $\cI_Z$ has bigger $(x,y)$ slope than $\cO_S(-C)[1]$.

By openness of stability, we just need to guarantee $I_Z$ is stable at a point on the line through $I(I_Z)$ and $I(\cO_S(-C)[1])$ intersected with the parabola. By lemma \ref{large-volume-limit}, since $I_Z$ is $H$-stable torsion free, we at least know $I_Z$ is semistable at $(x,-\mu(F)+\eps)$ for $x\gg 0$ and $0<\eps \ll 1$, i.e., $I_Z$ is stable in some circular sector bounded by the positive $x$-axis and some positie slope ray.

So, we just need to show that $F$ \textit{remains} stable through the ray from $I(I_Z)$ to $I(\cO_S(-C)[1])$.

\begin{center}
\begin{tikzpicture}[
        scale=0.6,
        extended line/.style={shorten >=-#1,shorten <=-#1}
    ]
    \draw[<->] (-3.5, 0) -- (10.4, 0) node[right] {$x$};
    \draw[<->] (0, -4.5) -- (0, 4.5) node[above] {$y$};
    \fill[variable=\y, domain=-4.5:4.5, smooth, color=gray, opacity=0.4]  -- plot ({0.5*\y*\y}, {\y}) -- cycle;

    \node (A) at (-1,0) {};
    \node (B) at (8,4) {};

    \filldraw[black] (B) circle (2pt) node[anchor=south east, fill=white, behind path] {$I(\cO_S(-C)[1])$};

    \filldraw[black] (A) circle (2pt) node[anchor=south east, fill=white, behind path]{$I(I_Z)$};

    \draw[<->,extended line=2cm] (A) -- (B);
\end{tikzpicture}
\end{center}

Now, for a point $(x,y)$ on a destabilizing wall for $I_Z$, choose a witness \(
    \begin{tikzcd} F \rar[hook,"\phi"]& I_Z\end{tikzcd}
\) (again as in lemma \ref{destabilizing-wall-witness}). We will refer to $\rk F$ as the \textit{rank of the wall} for $I_Z$ through $I(F)$. We want to establish numerical conditions on $(S,C)$ to prevent any walls that occur up to the $I_Z$, $\cO_S(-C)[1]$ wall. Our target wall has slope (in our coordinates for $\Stab(S)$)
\[m = \frac{\|C\|}{\frac{C^2}{2}+d} = \frac{2\|C\|}{C^2+2d},\]
so we want to guarantee that any other wall through $I_Z$ has greater slope.

\subsubsection{Higher Rank Walls}

Suppose $\rk F = r > 1$. As in \cite{bertram_two_2026}, we show that this implies the wall $W$ has too great a ``height'', i.e., showing that the ratio of the $y$ coordinates of the top intersection and bottom intersection of $W \cap \{x=\frac{1}{2}y^2\}$ is too large.

\begin{computation}
    For comparison, we compute this height ratio for the $I_Z, \cO_S(-C)[1]$ wall. The top intersection has $y$ coordinate $\|C\|$. The bottom intersection has is one of the solutions to the equations
    \[2x=y^2, \qquad y=m(x+d),\]
    which has $y$-coordinate which is a root of
    \begin{align*}
        y&=m\left(\frac{1}{2}y^2\right)+md\\
        0&=y^2-\frac{2}{m}y+2d.
    \end{align*}
    Since one root is $\|C\|$, the other root is $\frac{2d}{\|C\|}$. Thus, the height ratio is $\frac{C^2}{2d}$ (or potentially the reciprocal if $\|C\|$ isn't sufficiently large---but we will eventually require $\|C\|$ to be large enough so that $\|C\|$ is the bigger height).
\end{computation}

\bigskip





Now, we bound the height ratio for a rank $r$ wall. By Lemma \ref{between-parabola}, $I(F)$ is positioned between $I(I_Z)$ and the parabola, with positive $y$-value. Writing $E$ for the cone, so that we have exact sequence
\[0\to F \to I_Z \to E \to 0 \tag{$\star$}\]
in $\cA_{-y}$ (where $(x,y)$ is on the destabilizing wall). Since $F, I_Z$ are both $(x,y)$-semistable of the same slope, so is $E$. In this setup, $I(I_Z)$, $I(F)$, $(x,y)$, and $I(E)$ are all on the same line, and we at least know $I(I_Z)$ below $I(F)$ below $(x,y)$. Furthermore, by $(x,y)$ stability, $I(F),I(E)$ are outside the parabola.

\begin{prop}
    $I(E)$ is above $(x,y)$.
\end{prop}

\begin{proof}
    We have to show $\mu(E)<-y$. We know that $E\in D^b(S)$ has cohomology sheaves
    \[\cH^{-1}(E) = \ker_{\Coh(S)} \phi, \qquad \cH^0(E) = \coker_{\Coh(S)} \phi.\]
    Since $\phi\neq 0$ for $\phi$ to be a monomorphism, we in fact get
    \[\rk(\coker_{\Coh(S)} \phi) = 0\]
    since $\coker_{\Coh(S)} \phi = I_Z/\im_{\Coh(S)} \phi$ is a quotient of rank 1 sheaves, where $\im_{\Coh(S)}$ is rank 1 because it is a nonzero subsheaf of a torsion free sheaf. Thus, $\coker_{\Coh(S)} \phi$ is a torsion sheaf, and in particular
    \[c_1(\coker_{\Coh(S)} \phi) \geq 0\]
    is effective, since $c_1=\ch_1$ can be computed by taking lengths of $\coker_{\Coh(S)} \phi$ at generic points of components of the support (i.e., filter $\coker_{\Coh(S)} \phi$ by structure sheaves of curves and points by analyzing associated primes/points).

    On the other hand, $\rk(\ker_{\Coh(S)} \phi) = -\rk F$, since $\rk F$ is the alternating sum of the ranks of its cohomologies.

    Thus, we can compute
    \[\mu(E) = \mu(\ker_{\Coh(S)} \phi) + \frac{H\cdot c_1(\coker_{\Coh(S)} \phi)}{\rk F} \leq \mu(\ker_{\Coh(S)} \phi) \leq -y,\]
    since $H\cdot c_1(\coker_{\Coh(S)} \phi)\geq 0$, but $\rk F<0$. So, $-\mu(E) \geq y$, but this places $I(E)$ above $(x,y)$, so it must be above the parabola.
\end{proof}

Thus, the heights of $I(F)$, $I(E)$ give lower and upper bounds respectively on the height for this wall, so the height ratio is bounded above by
\[\frac{-\mu(E)}{-\mu(F)} = \frac{r}{r-1},\]
which among integer values $r>1$ is maximized at $r=2$ to get get a maximum height ratio of $2$. Thus, to prevent high rank walls from destabilizing $I_Z$ too early, we just need to require
\[\frac{r}{r-1} < \frac{C^2}{2d},\]
which is to require
\[C^2 > 4d.\]

\subsubsection{Rank 1 Walls}

Now, assume $\rk F = r = 1$. First, we characterize such sheaves $F$.

\begin{lem}
    A rank 1 sheaf on a smooth projective surface is of the form
    \[\cO(-E)\otimes I_W.\]
\end{lem}
\begin{proof}
    To see this, notice that $F^{\vee \vee}$ is a line bundle by virtue of being reflexive rank 1 on a smooth variety, and the usual evaluation map $s \mapsto \eval_s$ is injective in $\Coh(S)$, giving us the short exact sequence
    \[0\to F \xrightarrow{e} F^{\vee \vee} \to \coker e \to 0.\]
    Twisting by the dual $F^{\vee}$, we get
    \[0\to F \otimes F^{\vee} \to \cO_S \to \coker e \otimes F^{\vee} \to 0,\]
    which expresses $F$ as a twist of an ideal sheaf (being a subsheaf of $\cO_S$), and the Chern invariants will force it to be the ideal sheaf of a dimension 0 scheme.
\end{proof}


Next, when analyze stability, we will be interested in morphisms $I_W\to I_Z$, so we prove this next lemma.


{\color{red} is this even helpful here?}
\begin{lem}
    Let $Z,W$ be closed subschemes of codimension at least 2 in a smooth projective variety $X$. Then, $\Hom(I_W,I_Z)$ is $\C$ (spanned by inclusion) if $Z\subseteq W$ and 0 otherwise.
\end{lem}
\begin{proof}
    Let $\phi: I_W\to I_Z$. The strategy is to analyze double duals. First, we argue that $I_W^{\vee\vee},I_Z^{\vee\vee} \cong \cO_X$ by applying $\cHom_{\cO_X}(-,\cO_X)$ to, for example,
    \[0\to I_W \to \cO_X \to \cO_W \to 0\]
    and trying to get vanishing
    \[\cHom_{\cO_X}(\cO_W,\cO_X),\; \cExt^1(\cO_W,\cO_X)=0.\]
    First, $\cHom$ vanishes because there is no nonzero assignment of any $1\in \cO_W(U)$ to a section of $\cO_X$ due to torsion. Next, $\cExt_{\cO_X}^1(\cO_W,\cO_X)$ can be computed by the spectral sequence (for the composition of functors $R\Gamma$ and $R\cHom$)
    \[H^p(X,\cExt_{\cO_X}^q(\cO_W,\cO_X)) \Rightarrow \Ext^{p+q}(\cO_W,\cO_X),\]
    where {\color{red} how does this get vanishing? I might need something else}.

    Then, we form a commutative diagram
    \[\begin{tikzcd}
        I_W \rar["\phi"] \dar & I_Z \dar\\
        I_W^{\vee\vee} \rar["\phi^{\vee\vee}"] & I_Z^{\vee\vee}
    \end{tikzcd}\]
    where the vertical maps send $s\mapsto \eval_s$. In fancier language, $(-)^{\vee\vee}$ is an endofunctor, and $s\mapsto \eval_s$ is a natural transformation from identity.
    
    Now, the bottom morphism in our commutative diagram has to be multiplication by a constant $c\in \C$, and a nonzero $c$ also forces the top morphism $I_W\to I_Z$ uniquely to be $c$ multiplied by inclusion (in particular showing $Z\subseteq W$).

    (from \href{https://mathoverflow.net/questions/458245/homomorphism-between-ideal-sheaves-of-codimension-2}{this math overflow post})
\end{proof}


{\color{red} prove something like this?}
\begin{lem}\label{rank-1-destabilizer-morphism}
    A morphism $\cO_S(-E)\otimes I_W \to I_Z$ is the data of a section of $(I_Z: I_W)(E)$.
\end{lem}
\begin{proof}
    {\color{red} TODO}/
\end{proof}

Now, that we have a grip on the players, we try to handle stability. Our task is to rule out sheaves $\cO_S(-E)\otimes I_W$ before the numerical wall through $I(I_Z)$ and $I(\cO_S(-C)[1])$.

By lemma \ref{rank-1-destabilizer-morphism}, if we have already ruled out destabilizers of lower length schemes $Z'$ than $Z$, then we can assume $W=\emptyset$, since a morphism $\cO_S(-E)\otimes I_W \to I_Z$ will correspond to a
\[\cO_S(-E) \to (I_Z:I_W)=I_{Z'}\]
which is at least as ``dangerous'' as far as stability goes.

So, we are considering



\printbibliography


\end{document}